Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-10-28 demystify.tex
updates

However, in general, retracting an acceptance can have ethical implications. When you accept an offer, you are committing to work with that prof, who then might stop looking for other students. So by retracting your offer, you are breaking your commitment and also causing a great deal of inconvenience to the prof and also taking away the opportunity from other students. 
Ultimately, this choice is personal, involving a balance between personal benefit and the ethical impact on others.

@@

It is unlike that you can negotiate TA stipend, which is set by the university. Moreover, while RA is set by the adviser, it is often based on the department's standard, and it also would be unfair to other students if you get more (especially since you're new and have not proven yourself yet). However, your stipend is often increased every year by the university (automatically by a small amount).

@@

However, note this is a privilege and a courtesy and not a right.  This means that the prof. is not obligated to buy you things, and that you should not expect these are automatically provided.  Also, while the prof. might be able to do so in the past, they might not be able to do so now due to budget constraints.  It might also a need-based decision, e.g., if you need a powerful computer for your research, then the prof. might buy it for you (the lab might already has powerful servers and you can just use them for your work). Finally, the prof. might have a policy on what they can buy for you, e.g., they prefer to get you desktop instead of a laptop (to encourage you to come to the office and work).

@@

\subsubsection*{Additional Resources}
\begin{itemize}
  \item \href{https://www.cs.columbia.edu/wp-content/uploads/2019/03/Get-Advisor.pdf}{The Definitive ``what do I ask/look for'' in a PhD Advisor Guide}
\end{itemize}
\subsection{Who can serve as a PhD adviser?}\label{sec:faculty-types}

@@

@@

  \item[Advisor/Supervisor]: A faculty member who guides and mentors a PhD student throughout their research. This person typically plays a crucial role in a student's academic journey. In the US, the term ``adviser'' is more commonly used than ``supervisor''.

>>>>

However, in general, retracting an acceptance can have ethical implications. When you accept an offer, you are committing to work with that prof, who then might stop looking for other students. So by retracting your offer, you are breaking your commitment and also causing a great deal of inconvenience to the prof and also taking away the opportunity from other students. 
Ultimately, this choice is personal and involves a balance between personal benefit and ethical considerations.

@@

It is unlike that you can negotiate TA stipend (\autoref{sec:ta}), which is set by the university. Moreover, while RA is set by the adviser (\autoref{sec:ra}), it is often based on the department's standard, and it also would be unfair to other students if you get more (especially since you're new and have not proven yourself yet). However, your stipend is often increased every year by the university (automatically by a small amount).

@@

However, note this is a privilege and a courtesy and not a right.  Your prof. is not obligated to buy you things, and that you should not expect these are automatically provided.  Also, while the prof. might be able to do so in the past, they might not be able to do so now due to budget constraints.  It might also a need-based decision, e.g., if you need a powerful computer for your research, then the prof. might buy it for you (the lab might already has powerful servers and you can just use them for your work). Finally, the prof. might have a policy on what they can buy for you, e.g., they prefer to get you desktop instead of a laptop so that you come and work in the lab.

@@

\subsubsection*{Additional Resources}
\begin{itemize}
  \item \href{https://www.cs.columbia.edu/wp-content/uploads/2019/03/Get-Advisor.pdf}{The Definitive ``what do I ask/look for'' in a PhD Adviser Guide}
\end{itemize}
\subsection{Who can serve as a PhD adviser?}\label{sec:faculty-types}

@@

\section{Are profs. very busy (and therefore ghost me)?}\label{sec:busy}

Yes, profs. are busy. They have many deadlines, meetings, and emails, many of which are from prospective students looking for research opportunities.  Tenure-line profs. (\autoref{sec:faculty-types}) typically have 5 jobs (research, teaching, service, grant writing, and mentoring students). They also have a life outside of work, e.g., family, hobbies, etc.  So yes, they are super busy.

However, this is not why they ``ghost'' you. The main reason is that they are not interested. They might not have funding, the bandwidth to take on new students, or they might not be interested in your background. So don't take it personally if you don't get a reply.  If you want to increase your chance of getting a reply, see \autoref{sec:contact}.

\begin{commentbox}{Vu}
I scan through \emph{every single email} sent by students for research opportunities (many of which are from undergrads and highschool students). However, I only reply to those that I think are a good fit and ask them to chat with me. I tend to be more responsive to undergrads and highschool students , especially those in the local area, to encourage them to pursue research.  
\end{commentbox}

@@

  \item[Adviser/Superviser]: A faculty member who guides and mentors a PhD student throughout their research. This person typically plays a crucial role in a student's academic journey. In the US, the term ``adviser'' is more commonly used than ``supervisor''.
